BVP Methods

### 2017-11-21 notes/method_description/bvp_method.tex
update

So, put simply, the BVP that we need to solve in RBC is 
\begin{equation}
\begin{split}
\frac{\partial T_1}{\partial z} - T_{1z} &= 0 \\
\kappa \frac{\partial T_{1z}}{\partial z} &= \frac{\partial}{\partial z} \angles{w T}  - \kappa \frac{\partial^2 T_0}{\partial z^2}\\
\frac{\partial p}{\partial z} - T_1 &= 0.
\end{split}
\end{equation}
These three equations, coupled with two properl thermal boundary conditions, retrieve the full
thermodynamic state of the atmosphere.  I've written the equations in their dedalus-like form,
for clarity.

In a real way, the profile of the enthalpy flux thus sets the profile of the thermal structure of
the atmosphere.

>>>>

So, put simply, the BVP that we need to solve in RBC is 
\begin{equation}
\begin{split}
\frac{\partial T_1}{\partial z} - T_{1z} &= 0 \\
\kappa \frac{\partial T_{1z}}{\partial z} &= \frac{\partial}{\partial z} \angles{w T}  - \kappa \frac{\partial^2 T_0}{\partial z^2}\\
\frac{\partial p}{\partial z} - T_1 &= 0.
\end{split}
\end{equation}
These three equations, coupled with two properl thermal boundary conditions, retrieve the full
thermodynamic state of the atmosphere.  I've written the equations in their dedalus-like form,
for clarity.  I'll solve using fixed temp (top) and fixed flux (temp gradient, bottom) boundary
conditions.  Dual fixed-flux boundary conditions will work as well, but then the integrated temperature
profile's constant is actually not unique, so that system has degenerate answers that work for
the BVP.

In a real way, the profile of the enthalpy flux thus sets the profile of the thermal structure of
the atmosphere.  In order for this method to work, the profile of the enthalpy flux fed into the
BVP must be the enthalpy flux profile that we expect in the fully evolved atmosphere.  Getting
this profile properly is really the subtle part of this method, so let's talk about that.
